---
title: "CB vs APB Bulk RNAseq"
output: html_notebook
---

First install our packages.

```{r}
if (!require("BiocManager", quietly = TRUE))
  install.packages("BiocManager")

BiocManager::install("DESeq2")
BiocManager::install("apeglm")
BiocManager::install("IHW")
BiocManager::install("EnsDb.Hsapiens.v79")
install.packages("reshape2")
install.packages("RColorBrewer")
install.packages("pheatmap")
install.packages("stringr")
install.packages("dplyr")
BiocManager::install("ComplexHeatmap")

library(edgeR)
library(stringr)
library(ggplot2)
library(ggrepel)
library(dplyr)
library(tidyverse)
library(cowplot)
library(extrafont)
library(ggalt)
library(ggforce)
library(DESeq2)
library('biomaRt')
library(dplyr)
library(apeglm)
library("reshape2")
library(stringr)
library(ComplexHeatmap)

```

Clean the raw counts data by removing unwanted donors (AS, FS, PS), as well as sex genes (ChX, ChY). Make sure that whatever we keep match with meta data 
```{r}
adjusted_counts <- read.csv("adjusted_counts.csv")
meta <- read.csv("meta.csv")

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

